Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-02-13 Writing/CEA_2nd_round/replies_rev_1.rmd
minor changes

We believe that the detailed presentation of data generation is crucial in our reporting of MC procedures, as it would be in the report of any empirical study using real experiment data provides. In both cases, results are highly dependent procedures. We believe further slimming of the description would hinder anyone attempting to reproduce our results. That said, we have worked hard to remove redundancies in this section of the manuscript. 
</span>

@@

<span style="color:blue">  
We have followed the Editor's suggestion by sharing the simulation codes and the data on Mendeley Data (https://data.mendeley.com/datasets/y7cdhzww6w/draft?a=2e33b309-ca5c-49bc-95ce-9b3920d5544a) to increase the accessibility. The name of the data set is "Codes and Data Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation", and two folders are included in this data set: "Codes" and  "Data". The "Code" folder contains all the simulation codes, and the "Data" folder contains a boundary polygon data of a field which is necessary to create field data for this study. Please read README.md for the steps to reproduce. In addition, we created a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA))
</span>

@@

<span style="color:blue">  
We have added a section called “Limitations and Future Studies” before the Conclusion section of the revised manuscript. One of the important conditions for CF to provide consistent estimation of treatment effects is that the treatment (N rates here) is uncorrelated with unobservable characteristics. Other assumptions are relatively minor. Note that, this is not just for CF, but also for RF, BRF, and CNN. Whenever the variable of interest (N rates here), their estimation of its impact on the dependent variable is biased in general. Fortunately, in OFPE settings we can randomize or geographically pattern input rates to make them uncorrelated with unobserved variables. Therefore, the violation of this assumption is not as much of a concern as in a setting where observational data is used. We discuss these in the “Trial Design and Yield Data Generation for Modeling” section. 
</span>

>>>>

We believe that the detailed presentation of data generation is crucial in our reporting of MC procedures, as it would be in the report of any empirical study using real experiment data provides. In both cases, results are dependent procedures. We believe further slimming of the description would hinder anyone attempting to reproduce our results. That said, we have worked hard to remove redundancies in this section of the manuscript. 
</span>

@@

<span style="color:blue">  
We have followed the Editor's suggestion by sharing the simulation codes and the data on Mendeley Data (https://data.mendeley.com/datasets/y7cdhzww6w/draft?a=2e33b309-ca5c-49bc-95ce-9b3920d5544a) to increase the accessibility. The name of the data set is "Codes and Data Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation", and two folders are included in this data set: "Codes" and  "Data". The "Code" folder contains all the simulation codes, and the "Data" folder contains a boundary polygon data of a field which is necessary to create field data for this study. Please read README.md for the steps to reproduce. In addition, we also created a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
</span>

@@

<span style="color:blue">  
We have added a section called “Limitations and Future Studies” before the Conclusion section of the revised manuscript. One of the important conditions for CF to provide consistent estimation of treatment effects is that the treatment (N rates here) is uncorrelated with unobservable characteristics. Other assumptions are relatively minor. Note that, this is not just for CF, but also for RF, BRF, and CNN. Whenever the variable of interest (N rates here) is correlated with the unobservables (error term), their estimation of its impact on the dependent variable is biased in general. Fortunately, in OFPE settings we can randomize or geographically pattern input rates to make them uncorrelated with unobserved variables. Therefore, the violation of this assumption is not as much of a concern as in a setting where observational data is used. We discuss these in the “Trial Design and Yield Data Generation for Modeling” section. 
</span>

### 2022-02-13 Writing/appendix.rmd
minor changes

Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project. (Codes used to generate parameter values are available at @Kakimoto2022codes.) The range and nugget of all parameters were assumed to be $400$ m and 0. The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$. See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.

@@

For scenarios "aabbyy" and "aabbyytt," each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner. Specifically, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r^{\alpha}_{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r^{\beta}_{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r^{ymax}_{i,j} \in (0,1)$ to the ${ymax}_{i,j}$ variable. Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters. (There was no spatial correlation between the $r^{\alpha}_{i,j}$ and $r^{\beta}_{i,j}$ data, between $r^{\alpha}_{i,j}$ and $r^{ymax}_{i,j}$ data, or between $r^{\beta}_{i,j}$ and $r^{ymax}_{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha_{i,j}$, $\beta_{i,j}$ and $ymax_{i,j}$. These were 
$\alpha^{1}_{i,j} = r^{\alpha}_{i,j} \cdot \alpha_{i,j}$, $\alpha^{2}_{i,j} = (1- r^{\alpha}_{i,j}) \cdot \alpha_{i,j}$,
$\beta^{1}_{i,j} = r^{\beta}_{i,j} \cdot\beta_{i,j}$, $\beta^{2}_{i,j} = (1- r^{\beta}_{i,j}) \cdot\beta_{i,j}$,
$ymax^{1}_{i,j} = r^{ymax}_{i,j} \cdot ymax_{i,j}$, and $ymax^{2}_{i,j} = (1- r^{ymax}_{i,j}) \cdot ymax_{i,j}$. The codes used to implement the abovementioned parameter splitting is available at @Kakimoto2022codes.

>>>>

Table \@ref(tab:variogram-parameters) shows the main variogram parameter values used in generating $\alpha_{i,j}$, $\beta_{i,j}$, $ymax_{i,j}$, and $\varepsilon_{i,j}$, which were chosen to generate yields consistent with those observed in experiments conducted by the DIFM project. (Codes used to generate parameter values are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].) The range and nugget of all parameters were assumed to be $400$ m and 0. The means of $ymax$, $\alpha$, $\beta$, and $\varepsilon$ were assumed to be $12,000$ kg/ha, $-0.5$, $0$ and $0$, and their sills were assumed to be $2.0 \times 10^{6}$ kg/ha, $0.02$, $1.0$ and $0.015$. See Figure \@ref(fig:fig-parameters) for an example of the generated parameters.

@@

For scenarios "aabbyy" and "aabbyytt," each of the base parameters $\alpha$, $\beta$, and $ymax$ are splitted into two part in a spatially correlated manner. Specifically, for each cell $(i,j)$, we assigned one of a set of spatially autocorrelated weights $r^{\alpha}_{i,j} \in (0,1)$ to the $\alpha$ variable, another set of spatially autocorrelated weights $r^{\beta}_{i,j} \in (0,1)$ to the $\beta$ variable, and another set of spatially autocorrelated weights $r^{ymax}_{i,j} \in (0,1)$ to the ${ymax}_{i,j}$ variable. Each of the weight variables are generated using unconditional Gaussian geostatistical simulation just like the base parameters. (There was no spatial correlation between the $r^{\alpha}_{i,j}$ and $r^{\beta}_{i,j}$ data, between $r^{\alpha}_{i,j}$ and $r^{ymax}_{i,j}$ data, or between $r^{\beta}_{i,j}$ and $r^{ymax}_{i,j}$.) Six new covariates were created with the weights and the original covariates $\alpha_{i,j}$, $\beta_{i,j}$ and $ymax_{i,j}$. These were 
$\alpha^{1}_{i,j} = r^{\alpha}_{i,j} \cdot \alpha_{i,j}$, $\alpha^{2}_{i,j} = (1- r^{\alpha}_{i,j}) \cdot \alpha_{i,j}$,
$\beta^{1}_{i,j} = r^{\beta}_{i,j} \cdot\beta_{i,j}$, $\beta^{2}_{i,j} = (1- r^{\beta}_{i,j}) \cdot\beta_{i,j}$,
$ymax^{1}_{i,j} = r^{ymax}_{i,j} \cdot ymax_{i,j}$, and $ymax^{2}_{i,j} = (1- r^{ymax}_{i,j}) \cdot ymax_{i,j}$. The codes used to implement the abovementioned parameter splitting are publicly accessible as a Mendeley dataset [@Kakimoto2022codes].
